---
output: github_document
---

# Install Package 
First, you have to install devtools package and adding to your library

```{r eval = FALSE}
install.packages("devtools")
library(devtools)
```

And then you can download UN package by tools that devtools provides

```{r eval = FALSE}
install_github("tunay5/UNData")
library(UN)
```

## data_flow()
data_flow() function will return a dataframe which includes dataflows in UN database, the names of each dataflow and other (unimportant for your usage) details of each dataflow.

```{r eval = TRUE, include = FALSE}
install.packages("devtools", repos ="http://cran.us.r-project.org")
library(devtools)
install_github("tunay5/UNData")
library(UN)
```
 
 
```{r eval = FALSE}
data_flow()
```

```{r echo = FALSE}
data <- data_flow()

data <- data[,1:2]

data
```

## data_structure()
After selecting which dataflow you want to fetch data from, if you want to see the data structure, the informations on the data of selected dataflow, you should use \code {data_structure()} function. It will also assign the list of selected dataflow into your global environment.

Since this function returns a list of variables for the selected dataflow, to get the dataframe for a variable (COMMODITY variable for DF_UNDATA_ENERGY dataflow) use:

```{r eval = FALSE}
data_structure(dataflow = "DF_UNDATA_ENERGY")

list_DF_UNDATA_ENERGY$COMMODITY
```

```{r echo = FALSE}
data <- UN::data_structure("DF_UNDATA_ENERGY")

data_1 <- data$COMMODITY

data_1[1:10,]
```

## get_data()

With information that you accumulated from \code {data_structure()} function, you are able to fetch data based on these information.

Let's say you want to fetch the Environment data (DF_UNData_UNFCC dataflow) for Germany for the indicator of Methane (EN_ATM_METH_XLULUCF) between the years of 2010 and 2015:

```{r eval = FALSE}
get_data("DF_UNData_UNFCC", filter = list(c("REF_AREA","DEU"),c("INDICATOR", "EN_ATM_METH_XLULUCF")), start = 2010, end = 2015)

```

```{r eval = TRUE, include = FALSE}

data <- get_data("DF_UNData_UNFCC", filter = list(c("REF_AREA","DEU"),c("INDICATOR", "EN_ATM_METH_XLULUCF")), start = 2010, end = 2015)

```

```{r echo = FALSE}
data
```

## Notes

To learn more and understand the basics of how sdmx api of UNSD works, check out:

https://unstats.un.org/sdgs/files/SDMX_SDG_API_MANUAL.pdf

https://data.un.org/Host.aspx?Content=API
