---
output: github_document
---

# Install Package 
First, you have to install devtools package and adding to your library

```{r eval = FALSE}
install.packages("devtools")
library(devtools)
```

And then you can download UN package by tools that devtools provides

```{r eval = FALSE}
install_github("tunay5/UNData")
library(UN)
```

## data_flow()
data_flow() function will return a dataframe which includes dataflows in UN database, the names of each dataflow and other (unimportant for your usage) details of each dataflow.

```{r eval = TRUE, include = FALSE}
install.packages("devtools", repos ="http://cran.us.r-project.org")
library(devtools)
install_github("tunay5/UNData")
library(UN)
```
 
 
```{r eval = FALSE}
data_flow()
```

```{r echo = FALSE}
data <- data_flow()

data <- data[,1:2]

data
```

## data_structure()
After selecting which dataflow you want to fetch data from, if you want to see the data structure, the informations on the data of selected dataflow, you should use \code {data_structure()} function. It will also assign the list of selected dataflow into your global environment.

```{r eval = FALSE}
data_structure(dataflow = "DF_UNData_UNFCC")
```

```{r}

```

